\documentclass[12 pt,a4paper]{article}
\usepackage[a4paper, hmargin={2.8cm, 2.8cm}, vmargin={2.5cm, 2.5cm}]{geometry}
\usepackage[table,xcdraw]{xcolor}
\usepackage{eso-pic} % \AddToShipoutPicture
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage[english]{isodate}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{upgreek}
\usepackage{wrapfig}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{color}
\usepackage{subcaption}
\usepackage{csquotes}
\usepackage[figurename = Fig .]{caption}


\renewcommand{\comment}[1]{%
\text{\phantom{(#1)}} \tag{#1}
}

\newcommand{\Fin}{
\vfill
\begin{center}
\textit{ }\label{FIN}
\end{center}}


\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\rm \arabic{section}.\arabic{subsection}}
\renewcommand{\thesubsubsection}{\rm \arabic{subsubsection}}
\setcounter{tocdepth}{2}

\definecolor{listinggray}{gray}{0.9}
\lstset{
language=,
literate=
{æ}{{\ae}}1
{ø}{{\o}}1
{å}{{\aa}}1
{Æ}{{\AE}}1
{Ø}{{\O}}1
{Å}{{\AA}}1,
backgroundcolor=\color{listinggray},
tabsize=3,
rulecolor=,
basicstyle=\scriptsize,
upquote=true,
aboveskip={0.2\baselineskip},
columns=fixed,
showstringspaces=false,
extendedchars=true,
breaklines=true,
prebreak =\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
frame=single,
showtabs=false,
showspaces=false,
numbers=left,
showlines=true,
upquote=true,
showstringspaces=false,
identifierstyle=\ttfamily,
keywordstyle=\color[rgb]{0,0,1},
commentstyle=\color[rgb]{0.133,0.545,0.133},
stringstyle=\color[rgb]{0.627,0.126,0.941},
moredelim=**[is][\color{blue}]{@}{@},
}

\lstdefinestyle{base}{
emptylines=1,
breaklines=true,
basicstyle=\ttfamily\color{black},
}

\begin{document}
\noindent This is a workshop task sheet, 
that will let you experience some of the scenarios you will meet as a git user.
Throughout this task sheet,
you will probably need to consult the README.md or search the internet for solutions.

\section*{Starting git}
This is a task for you to explore the world of github.
Some of you might already have a user and all, 
but we will start from scratch.

\subsection*{First steps}
The advanced users can skip this,
but do read it through and see if you can learn something anyway.
\begin{enumerate}
  \item Make a user on github
  \item Install git on your machine
  \item Set up user info (user.name, user.email, user.editor) **OPTIONAL**
  \item Set up SSH key **OPTIONAL**
\end{enumerate}

\subsection*{Start your own project}
With git installed on our system, let us now start working on a project.
\begin{enumerate}
\item Make a repository
\item Clone your own repository to your machine
\item Make a README.md file and write some information
\item Push your changes
\end{enumerate}

\subsection*{Handling working with others}
Let us now for the purpose of experiencing conflicts, you will have to do as follows.

\begin{enumerate}
\item Make new directory
\item Clone your repository to that new directory
\item Add some changes to the files in your newly cloned directory
\item Push the changes to your repo
\item Go to your original directory, make some changes to that same file.
\item attempt to push those new changes
\item THIS IS MERGE CONFLICT 

\end{enumerate}

\Fin
\end{document}
